Formalizing Stack Safety as a Security Property

### 2022-08-26 submission5/onlyformalism.tex
Update

The underlying machine is a standard RISC-V ISA as modeled in [MIT-RISCV].
Our overlay semantics provide macro-instructions for the following code features:
\begin{itemize}
\item Function calls and returns, with caller- and callee-saved registers according
  to the RISC-V ABI
\item Arguments passed by reference
\item Exceptions
\item Coroutines and cooperative threading
\item Tail-call Elimination
\end{itemize}

\paragraph*{What is a ``call''?} Some ISAs have a single ``call''
instruction that does all the required manipulation of the program counter
(\(\PCname\)) and stack pointer; others perform a series of instructions
whose constituent opcodes may be used in some places for other purposes.
Our RISC-V machine is the latter, so calls must be explicitly designated
as such by the compiler, by identifying them as macro-instructions.
The same goes for other operations, such as exceptions and coroutine yields.
Macro-instructions connect the enforcement mechanism to the property: we don't
expect the enforcement mechanism to provide any guarantees for code sequences
that resemble calls or returns, but which are not macro-instructions.

Because macro-instructions must be generated by the compiler, they only
carry data that can be known by the compiler at compile-time. For example,
the \(\mathbf{call}\) macro-instruction identifies the register \(r\) containing
the address of the function to be called, as well as a {\it type record} identifying
the registers and addresses in which the callee expects to find arguments,
and a {\it public set}.
Let \(tr \in TR\) be a type record; then \(tr.args\) is a set of those registers
that will be used for arguments, and \(tr.stack\_args\) defines a set of
offsets from the stack pointer that are expected to contain additional
arguments.The public set \(pubs\) defines a similar set of offsets in
the caller that are declared public and not to be protected.

@@

In general, it is impossible to distinguish buggy source code from an attacker;
we assume nothing about the intent of the source code, except that it makes calls
and returns, and guarantee that the caller and callee are protected from one
another.

@@

We do not support dynamic code generation or concurrency---we can handle a
limited form of coroutines, but not full-blown preemptive concurrency.
[Say something about Heap Safety]

@@

The building blocks of the machine are {\em words} and {\em registers}.
Words are 64-bit integers ranged over by \(w\) and, when used as addresses,
\(a\). Each processor has 32 registers, ranged over in general by \(r\),
plus a program counter (\(\PCname\)). The following table divides
the registers into metavariables, some belonging to caller- or callee- sets:

@@

We specify that a register belongs to processor \(\rho \in \mathcal{R}\) by writing
it \(r^\rho\), but will omit this notation when the active
processor is unambiguous from context.

Collectively addresses and registers are {\em state elements} \(\component\)
in the set \(\COMPONENTS ::= \WORDS + \REGS\).
%
A {\em machine state} \(\mach \in \MACHS ::= \COMPONENTS \rightarrow \WORDS\)
is a mapping from state elements to values. For convenience, we abbreviate
multiple updates \(m[\component_0 \mapsto \word_0][\component_1 \mapsto \word_1]\dots\)
as \(m \llbracket A \mapsto B | C \rrbracket\), where \(A\) and \(B\)
are fomulae with free variables bound to sets in \(C\).
The base machine step relation 
\(\mach \harpoonunder{\rho}_M \mach' \subseteq \MACHS \times \mathcal{R} \times \MACHS\)
represents a single step of the processor \(\rho\).

The machine is equipped with additional state representing the tag-based hardware.
We represent this as a policy state, \(\pol \in \POLS ::= \COMPONENTS \rightarrow \mathcal{T}\),
where \(\mathcal{T}\) is the set of tags, discussed [in the section on security.]
We represent a {\it policy} via the step relation
\(\mach, \pol \harpoonunder{\rho}_P \pol' \subseteq \MACHS \times \POLS \times \mathcal{R} \times \POLS\).
Steps are deterministic and  undefined represents a {\it failstop}.

Separate from the machine state, we keep track of additional security context
information over the course of the run. This data is not relevant to execution,
it is only used to define the stack safety property. We define a set of
{\it security classes}:
\[sc \in SEC ::= \sealed | \mathit{object}(\phi) | \unsealed\]
And of {\it targets}, which identify the addresses of the program counter or
stack pointer at a return or catch point:
\[\begin{split}
tar \in TAR ::= & \mathit{Return} ~ a_{pc} ~ a_{sp} \\
| & \mathit{Catch} ~ a_{pc} ~ a_{sp} \\
\end{split}\]
A {\it security view} \(V \in \mathit{VIEW} ::= \COMPONENTS \rightarrow SEC\) divides the machine
elements in terms of their purpose relative to the active function.
And a {\it stack context} is a stack of pairs of targets and views:
\[\context \in \CONTEXTS ::= \mathit{list} ~ (\mathit{TAR} \times \mathit{VIEW})\]

Our properties additionally depend on a rudimentary model of memory-safe
objects and pointer provenance. A provenance \(\phi \in \mathbb{N}\)
identifies a value derived from the \(\phi\)th object allocated since
the beginning of execution. A provenance map
\(\prov \in \PROVS ::= \COMPONENTS \rightarrow 2^{\mathbb{N}}\)
designates, for every machine element, which provenances its current
value contains. We define a step relation on provenance maps
\(\mach, \prov \harpoonunder{\rho}_{pm} \prov' \subseteq \MACHS \times
\PROVS \times \mathcal{R} \times \PROVS\),
exerpted in Figure \ref{fig:provenance} [TODO].

The set of instructions, \(I \subseteq \WORDS\), corresponds to the RISC-V ISA.
We further introduce {\it overlay sequences}: sequences of
instructions that operate as if they were single, atomic pseudoinstructions.
An overlay sequence consists of both a list
of instructions and a pseudoinstruction that identifies its purpose in the
property. The pseudoinstructions, and the data that they carry, are as follows.
[TODO: still handle stack args by offset.]

@@

An overlay sequence \(j \in J\) is a pair of a pseudoinstruction and
a non-empty list of instructions.

\judgmentthree{\(\mach \harpoonunder{\rho}_M \mach'\)}
              {\(\mach, \pol \harpoonunder{\rho}_P \pol'\)}
              {\(\mach, \prov \harpoonunder{\rho}_{pm} \prov'\)}
              {\((\mach,\pol,\prov) \stepstounder{\rho} (\mach',\pol',\prov')\)}

And we define a {\it ranged-step} relation that, given a pair of addresses
\(a_{low}\) and \(a_{high}\), steps as long the program counter is between them.

@@

Now we're finally ready to introduce the overlay semantics.
A {\it full state} \(\sigma\) consists of a 4-tuple of a machine state,
a policy state, a provenance map, and a stack context:
\[\sigma = (\mach, \pol, \prov, ctxs) \in \mathcal{S} ::=
\MACHS \times \POLS \times \PROVS \times (\mathcal{R} \rightarrow \CONTEXTS)\]

The execution relation for full states
\(\sigma \stepstounder{\rho;\psi?} \sigma' \subseteq
\mathcal{S} \times \mathcal{R} \times (\Psi + \bot) \times \mathcal{S}\)
proceeds by an {\it overlay step}
if the program counter points to the start of an overlay sequence.
Otherwise, it proceeds by the default step. The definitions of context steps
\(\harpoonunder{\rho;\psi}_C\) will be defined for each pseudoinstruction as we go.

\judgmenttwobrlongbrlong[Overlay]
                        {\(j = (\psi, \bar{i})\)}
                        {\(\mach',\prov',ctxs ~ \rho \harpoonunder{\rho;\psi}_C \context\)}
                        {\((\mach,\pol,\prov) \manystepstounder{\rho} (\mach',\pol',\prov')\)}
                        {\(\mach[\PCname+n] = \bar{i}[n]\) for each \(n\) where \(0 \leq n < |\bar{i}|\)}
                        {\((\mach,\pol,\prov,ctxs) \stepstounder{\rho;\psi} (\mach',\pol',\prov',ctxs[\rho \mapsto \context])\)}

@@

\paragraph*{Overlay sequence definitions}

@@

Note that there can be multiple overlay sequences with different instructions
that represent the same pseudoinstruction.
[This is less likely when we have smaller pseudoinstructions.]

\paragraph*{Concurrency}

Thus far, we have defined the step relation of a single processor.
We model multiple processors able to step independently by a global step relation,
\(\stepstounder{}\), which simply steps an arbitrary processor:

\judgment[]
         {\(\sigma \stepstounder{\rho} \sigma'\)}
         {\(\sigma \stepstounder{} \sigma'\)}

@@

In this section we will present the context steps for allocations,
calls, and returns, and show how they
translate into properties. They are given formally in Figure \ref{fig:callcontexts}.
Allocations are simple: from the current stack pointer, a range up to the size of
the allocation is marked \(\mathit{object}(\phi)\) for a fresh identifier \(\phi\).

@@

\begin{figure*}
\[\begin{split}
& \mathit{update\_view} ~ V ~ \prov ~ a_{sp} ~ \overline{r_{args}} \triangleq
\lambda \component .
\begin{cases}
  \mathit{public} & \textnormal{else if } \component \in \REGS \textnormal{ and }
  \component \in \overline{r_{args}} \textnormal{ or } \component \in \mathit{PUBLIC} \\
  \mathit{object}(\phi) & \textnormal{else if } (V ~ \component) = \mathit{object}(\phi)
  \textnormal{ and } \phi \in \mathit{reach} ~ \prov ~ V ~ \overline{r_{args}} \\
  \sealed & \textnormal{else if } \component \in \WORDS \textnormal{ and } a_{sp} < \component \leq a_{sbase} \\
  \unsealed & \textnormal{otherwise} \\
\end{cases} \\
\end{split}\]

\judgmenttwobrlong[CallC]
                  {\(\psi = \mathbf{call} ~ r_{target} ~ \overline{r_{args}}\)}
                  {\(\context' = (\mathit{Return} ~ (m[pc] + 4) ~ m[sp], V)::\context\)}
                  {\(V = \mathit{update\_view} ~ (snd ~ (hd\_def ~ \context)) ~ m[sp] ~ \overline{r_{args}}\)}
                  {\(\mach, \prov, \context \constep{\rho;\psi} \context'\)}

@@

\section{Stack Safety, Formally}
\label{sec:properties}

Now we can give our definition of stack safety. Each overlay sequence defines a
context step; in turn, the context at the point of a call or return defines a
property each for integrity, confidentiality, and well-bracketed control flow.

@@

\paragraph*{Event Traces}

Some steps of execution can be interpreted as {\it events} that can be observed
from outside the system. We define events \(\obs \in \OBSS\) as calls, labeled
with the target address and the values of the arguments, or else as the silent
event \(\tau\):
\[\begin{split}
\obs \in \OBSS ::= & ~ \mathbf{callE} ~ a_{target} ~ \overline{w_{args}} \\
| & ~ \tau \\
\end{split}\]

\begin{figure*}
\[\mathit{observe} ~ \rho ~ \psi? ~ m =
\begin{cases}
  (\rho, \mathbf{callE} ~ m[\PCname] ~ m \llbracket r | r \in \overline{r_{args}} \rrbracket)
  & \textnormal{when } ~ \psi = \mathbf{call} ~ r_{target} ~ \overline{r_{args}} \\
  (\rho, \mathbf{returnE} ~ m[\PCname] & \textnormal{when } \psi = \mathbf{return} \\
  (\rho, \tau) & \textnormal{otherwise} \\
\end{cases}\]
\caption{Converting overlay steps to events}
\label{fig:observe}
\end{figure*}

\judgmenttwo{\(\sigma \stepstounder{\rho; \psi?} \sigma'\)}
            {\(\sigma' \hookrightarrow \obsT\)}
            {\(\sigma \hookrightarrow \notfinished{(\mathit{observe} ~ \rho ~ \psi? (\pi_m{\sigma'}))}{\obsT}\)}

\paragraph*{Trace Until Return}

We define another relation that takes a trace of a callee up to its return, if one occurs.
We write this \(\context \downarrow \sigma \hookrightarrow \obsT\), where \(\context\)
is the context of the caller.

\judgment{\(\context = \pi_c(\sigma)\)}
         {\(\context \downarrow \sigma \hookrightarrow \tau\)}

\judgmentthree{\(\sigma \stepstounder{\rho,\psi?} \sigma'\)}
              {\(\context \not = \pi_c(\sigma')\)}
              {\(\context \downarrow \sigma' \hookrightarrow \obsT\)}
              {\(\context \downarrow \sigma \hookrightarrow \notfinished{(\mathit{observe} ~ \rho ~ \psi? (\pi_m{\sigma'}))}{\obsT}\)}

We say that two event traces $\obsT_1$ and $\obsT_2$ are {\em similar}
from the perspective of an external observer, written \(\obsT_1 \eqsim
\obsT_2\), if the sequence of non-silent events is the same. That is, we
compare up to deletion of \(\tau\) events, coinductively:

\begin{minipage}{.4\columnwidth}
  \judgment{}{\(\obsT \eqsim \obsT\)}
\end{minipage}
\begin{minipage}{.4\columnwidth}
  \judgment{\(\obsT_1 \eqsim \obsT_2\)}
           {\(\notfinished{\tau}{\obsT_1} \eqsim \obsT_2\)}
\end{minipage}

\begin{minipage}{.4\columnwidth}
  \judgment{\(\obsT_1 \eqsim \obsT_2\)}
           {\(\obsT_1 \eqsim \notfinished{\tau}{\obsT_2}\)}
\end{minipage}
\begin{minipage}{.4\columnwidth}
  \judgment{\(\obsT_1 \eqsim \obsT_2\)}
           {\(\notfinished{\obs}{\obsT_1} \eqsim \notfinished{\obs}{\obsT_2}\)}
\end{minipage}

@@

>>>>

The underlying machine is a standard RISC-V ISA as modeled in [MIT-RISCV].
Our overlay semantics provide macro-instructions for the following code features:
\begin{itemize}
\item Function calls and returns, with caller- and callee-saved registers according
  to the RISC-V ABI
\item Arguments passed by reference
\item Exceptions
\item Tail-call Elimination
\end{itemize}

\paragraph*{What is a ``call''?} Some ISAs have a single ``call''
instruction that does all the required manipulation of the program counter
(\(\PCname\)) and stack pointer; others perform a series of instructions
whose constituent opcodes may be used in some places for other purposes.
Our RISC-V machine is the latter, so calls must be explicitly designated
as such by the compiler, by identifying them as macro-instructions.
The same goes for other operations, such as exceptions.
Macro-instructions connect the enforcement mechanism to the property: we don't
expect the enforcement mechanism to provide any guarantees for code sequences
that resemble calls or returns, but which are not macro-instructions.

Because macro-instructions must be generated by the compiler, they only
carry data that can be known by the compiler at compile-time. For example,
the \(\mathbf{call}\) macro-instruction identifies the register \(r_{target}\) containing
the address of the function to be called, as well as the registers that hold arguments.

@@

In general, it is impossible to distinguish buggy source code from an attacker;
we assume nothing about the intent of the source code, except that it makes calls
and returns, and we must guarantee that the caller and callee are protected from one
another.

@@

We do not support dynamic code generation, and our concurrency model is fairly
simplistic, assuming a fixed number of threads each with its own dedicated processor.
We model memory safe stack objects, but not a heap. Regions outside of
stacks can be used however the compiler likes, including as a heap, but no protection is
built in and our properties assume that if a pointer to a stack object is stored there,
it is permanently compromised.

@@

The building blocks of the machine are {\em words} and {\em registers}.
Words (\(\WORDS\)) are 64-bit integers ranged over by \(w\) and, when used as addresses,
\(a\). Each processor has 32 registers, ranged over in general by \(r\),
plus a program counter (\(\PCname\)). The following table divides
the registers into metavariables, some belonging to caller- or callee- sets:

@@

We specify that a register belongs to processor \(\rho \in \PROCS\) by writing
it \(r^\rho\), but will omit this notation when the active
processor is unambiguous from context. The set of all registers across all processors
is \(\REGS\).

Collectively addresses and registers are {\em state elements} \(\component\)
in the set \(\COMPONENTS ::= \WORDS + \REGS\).
%
A {\em machine state} \(\mach \in \MACHS ::= \COMPONENTS \rightarrow \WORDS\)
is a mapping from state elements to values. For convenience, we abbreviate
multiple updates \(m[\component_0 \mapsto \word_0][\component_1 \mapsto \word_1]\dots\)
as \(m \llbracket A \mapsto B | C \rrbracket\), where \(A\) and \(B\)
are fomulae with free variables bound to sets in \(C\).
The base machine step relation 
\(\mach \machstep{\rho} \mach' \subseteq \MACHS \times \PROCS \times \MACHS\)
represents a single step of the processor \(\rho\).

The machine is equipped with additional state representing the tag-based hardware.
We represent this as a policy state, \(\pol \in \POLS ::= \COMPONENTS \rightarrow \mathcal{T}\),
where \(\mathcal{T}\) is the set of tags, discussed [in the section on security.]
We represent a {\it policy} via the step relation
\(\mach, \pol \harpoonunder{\rho}_P \pol' \subseteq \MACHS \times \POLS \times \PROCS \times \POLS\).
Steps are deterministic and  undefined represents a {\it failstop}.

Our properties additionally depend on a rudimentary model of memory-safe
objects and pointer provenance. A provenance \(\phi \in \mathbb{N}\)
identifies a value derived from the \(\phi\)th object allocated since
the beginning of execution. A provenance map
\(\prov \in \PROVS ::= \COMPONENTS \rightarrow 2^{\mathbb{N}}\)
designates, for every machine element, which provenances its current
value contains. We define a step relation on provenance maps
\(\mach, \prov \harpoonunder{\rho}_{pm} \prov' \subseteq \MACHS \times
\PROVS \times \PROCS \times \PROVS\),
exerpted in Figure \ref{fig:provenance} [TODO].

\judgmentthree{\(\mach \machstep{\rho} \mach'\)}
              {\(\mach, \pol \polstep{\rho} \pol'\)}
              {\(\mach, \prov \provstep{\rho} \prov'\)}
              {\((\mach,\pol,\prov) \stepstounder{\rho} (\mach',\pol',\prov')\)}

As the last piece of state, we keep track of security context information
specific to each stack
over the course of the run. This data is not relevant to execution,
it is only used to define the stack safety property. We define a set of
{\it security classes}:
\[sc \in SEC ::= \public | \sealed | \mathit{object}(\phi) | \unsealed\]
And of {\it targets}, which identify the addresses of the program counter or
stack pointer at a return or catch point:
\[\begin{split}
tar \in TAR ::= & \mathit{Return} ~ a_{pc} ~ a_{sp} \\
| & \mathit{Catch} ~ a_{pc} ~ a_{sp} \\
\end{split}\]
A {\it security view} \(V \in \mathit{VIEW} ::= \COMPONENTS \rightarrow SEC\) divides the machine
elements in terms of their purpose relative to the active function.
And a {\it stack context} is a stack of pairs of targets and views:
\[\context \in \CONTEXTS ::= \mathit{list} ~ (\mathit{TAR} \times \mathit{VIEW})\]

The set of instructions, \(I \subseteq \WORDS\), corresponds to the RISC-V ISA.
We further introduce {\it macro-instructions}: sequences of
instructions that operate as if they were single, atomic pseudoinstructions.
A macro-instruction consists of both a list
of instructions and a pseudoinstruction that identifies its purpose in the
property. The pseudoinstructions, and the data that they carry, are as follows.
[TODO: still handle stack args by offset.]

@@

An macro-instruction \((\bar{i},\psi) \in J\) is a pair of a pseudoinstruction and
a non-empty list of instructions. In order to implement the atomic nature of
executing macro-instructions,
we define a {\it ranged-step} relation that, given a pair of addresses
\(a_{low}\) and \(a_{high}\), steps as long the program counter is between them.

@@

Now we're finally ready to introduce the overlay semantics.
A {\it full state} \(\sigma\) consists of a 4-tuple of a machine state,
a policy state, a provenance map, and a map from processors to stack contexts:
\[\sigma = (\mach, \pol, \prov, ctxs) \in \mathcal{S} ::=
\MACHS \times \POLS \times \PROVS \times (\PROCS \rightarrow \CONTEXTS)\]

The execution relation for full states
\(\sigma \stepstounder{\rho;\psi?} \sigma' \subseteq
\mathcal{S} \times \PROCS \times (\Psi + \bot) \times \mathcal{S}\)
proceeds by an {\it overlay step}
if the program counter points to the start of a macro-instruction.
Otherwise, it proceeds by the default step. The definitions of context steps
\(\constep{\rho;\psi}\) will be defined for each pseudoinstruction as we introduce
topics.

\judgmenttwobrlongbrlong[Overlay]
                        {\((\bar{i}, \psi) \in J\)}
                        {\(\mach',\prov',(ctxs ~ \rho) \constep{\rho;\psi} \context\)}
                        {\((\mach,\pol,\prov) \manystepstounder{\rho} (\mach',\pol',\prov')\)}
                        {\(\mach[\PCname+n] = \bar{i}[n]\) for each \(n\) where \(0 \leq n < |\bar{i}|\)}
                        {\((\mach,\pol,\prov,ctxs) \stepstounder{\rho;\psi} (\mach',\pol',\prov',ctxs[\rho \mapsto \context])\)}

@@

\paragraph*{Macro-instruction definitions}

@@

Note that there can be multiple macro-instructions with different instructions
that represent the same pseudoinstruction.
[This is less likely when we have smaller pseudoinstructions.]

\paragraph*{Concurrency and Traces}

So far we have defined the execution steps of single processors. Processors
have their own register banks, but share memory, and may step independently
in any order. We can represent sequences of these steps as traces.
Some steps of execution can be interpreted as {\it events} that can be observed
from outside the system. We define events \(\obs \in \OBSS\) as calls, labeled
with the target address and the values of the arguments, or else as the silent
event \(\tau\):
\[\begin{split}
\obs \in \OBSS ::= & ~ \mathbf{callE} ~ a_{target} ~ \overline{w_{args}} \\
| & ~ \tau \\
\end{split}\]

\begin{figure*}
\[\mathit{observe} ~ \rho ~ \psi? ~ m =
\begin{cases}
  (\rho, \mathbf{callE} ~ m[\PCname] ~ m \llbracket r | r \in \overline{r_{args}} \rrbracket)
  & \textnormal{when } ~ \psi = \mathbf{call} ~ r_{target} ~ \overline{r_{args}} \\
%  (\rho, \mathbf{returnE} ~ m[\PCname] & \textnormal{when } \psi = \mathbf{return} \\
  (\rho, \tau) & \textnormal{otherwise} \\
\end{cases}\]
\caption{Converting overlay steps to events}
\label{fig:observe}
\end{figure*}

\judgmenttwo{\(\sigma \stepstounder{\rho; \psi?} \sigma'\)}
            {\(\sigma' \hookrightarrow \obsT\)}
            {\(\sigma \hookrightarrow \notfinished{(\rho,\mathit{observe} ~ \rho ~ \psi? ~ \pi_m(\sigma'))}{\obsT}\)}

Naturally, most states will admit many possible traces, depending on the order in which
processors step.

We define another relation that takes a trace of a callee up to its return, if one occurs.
In this case we must specify that we are considering a single processor.
We write this \(\rho,\context \downarrow \sigma \hookrightarrow \obsT\), where \(\context\)
is the context of the caller.

\judgment{\(\context = \pi_c(\sigma) ~ \rho\)}
         {\(\rho, \context \downarrow \sigma \hookrightarrow \tau\)}

\judgmentthree{\(\sigma \stepstounder{\rho',\psi?} \sigma'\)}
              {\(\rho \not = \rho'\)}
              {\(\rho, \context \downarrow \sigma' \hookrightarrow \obsT\)}
              {\(\rho, \context \downarrow \sigma \hookrightarrow \obsT\)}

\judgmentthree{\(\sigma \stepstounder{\rho,\psi?} \sigma'\)}
              {\(\context \not = \pi_c(\sigma') ~ \rho\)}
              {\(\context \downarrow \sigma' \hookrightarrow \obsT\)}
              {\(\context \downarrow \sigma \hookrightarrow \notfinished{(\mathit{observe} ~ \rho ~ \psi? (\pi_m{\sigma'}))}{\obsT}\)}

We say that two event traces $\obsT_1$ and $\obsT_2$ are {\em similar}
from the perspective of processor \(\rho\), written \(\obsT_1 \eqsim_\rho
\obsT_2\), if the sequence of non-silent \(\rho\) events is the same. That is, we
compare up to deletion of \(\tau\) events and events from other processors, coinductively:

\begin{minipage}{.4\columnwidth}
  \judgment{}{\(\obsT \eqsim_\rho \obsT\)}
\end{minipage}
\begin{minipage}{.4\columnwidth}
  \judgment{\(\obsT_1 \eqsim_\rho \obsT_2\)}
           {\(\notfinished{(\rho, \obs)}{\obsT_1} \eqsim_\rho \notfinished{(\rho, \obs)}{\obsT_2}\)}
\end{minipage}

\begin{minipage}{.4\columnwidth}
  \judgment{\(\obsT_1 \eqsim_\rho \obsT_2\)}
           {\(\notfinished{(\rho,\tau)}{\obsT_1} \eqsim_\rho \obsT_2\)}
\end{minipage}
\begin{minipage}{.4\columnwidth}
  \judgment{\(\obsT_1 \eqsim_\rho \obsT_2\)}
           {\(\obsT_1 \eqsim_\rho \notfinished{(\rho,\tau)}{\obsT_2}\)}
\end{minipage}

\begin{minipage}{.4\columnwidth}
  \judgment{\(\obsT_1 \eqsim_\rho \obsT_2\)}
           {\(\notfinished{(\rho',\obs)}{\obsT_1} \eqsim_\rho \obsT_2\)}
\end{minipage}
\begin{minipage}{.4\columnwidth}
  \judgment{\(\obsT_1 \eqsim_\rho \obsT_2\)}
           {\(\obsT_1 \eqsim_\rho \notfinished{(\rho',\obs)}{\obsT_2}\)}
\end{minipage}

@@

In this section we will present the context steps for allocations,
calls, and returns, and show how they
translate into properties. They are given formally in Figure \ref{fig:callcontexts}.
Allocations are simple: from the current stack pointer, a range up to the size of
the allocation is marked \(\mathit{object}(\phi)\) for a fresh identifier \(\phi\).
[TODO: actually generate fresh \(\phi\) by keeping counter...]
[TODO: need to put the original \(\phi\) somewhere. Maybe macro-instruction
  for offsetting from stack pointer? Ugh.]

@@

\begin{figure*}
\judgmenttwobrlong[AllocC]
                  {\(\psi = \mathbf{alloc} ~ size\)}
                  {\((T,V) = (hd\_def ~ \context)\)}
                  {\(V' = V\llbracket m[sp]+i \mapsto \mathit{object}(\phi) | 0 < i \leq size \rrbracket\)}
                  {\(\mach, \prov, \context \constep{\rho;\psi} ctxs[\rho \mapsto (T,V')::(tl\_def ~ \context]\)}

\[\begin{split}
& \mathit{update\_view} ~ V ~ \prov ~ a_{sp} ~ \overline{r_{args}} \triangleq
\lambda \component .
\begin{cases}
  \mathit{public} & \textnormal{else if } \component \in \REGS \textnormal{ and }
  \component \in \overline{r_{args}} \textnormal{ or } \component \in \mathit{PUBLIC} \\
  \mathit{object}(\phi) & \textnormal{else if } (V ~ \component) = \mathit{object}(\phi)
  \textnormal{ and } \phi \in \mathit{reach} ~ \prov ~ V ~ \overline{r_{args}} \\
  \sealed & \textnormal{else if } \component \in \WORDS \textnormal{ and } a_{sp} < \component \leq a_{sbase} \\
  \unsealed & \textnormal{otherwise} \\
\end{cases} \\
\end{split}\]

\judgmenttwobrlong[CallC]
                  {\(\psi = \mathbf{call} ~ r_{target} ~ \overline{r_{args}}\)}
                  {\(\context' = (\mathit{Return} ~ (m[pc] + 4) ~ m[sp], V)::\context\)}
                  {\(V = \mathit{update\_view} ~ (snd ~ \context) ~ m[sp] ~ \overline{r_{args}}\)}
                  {\(\mach, \prov, \context \constep{\rho;\psi} \context'\)}

@@

Now we can give our definition of stack safety in terms of the context at the point of a call.

@@

@@

\paragraph*{Property Definitions}

And with the preliminary definitions out the way, we can define integrity.
